The Astropy Project

### 2017-10-26 main.tex
typo

The package also provides the a histogram function, which is a generalization of \package{matplotlib}’s histogram function, to allow for more flexible specification of histogram bins.  The function provides several methods of automatically tuning the histogram bin size. It has a syntax identical \package{matplotlib}’s histogram function (with the exception of the bins parameter), which allows specification of one of four different methods for automatic bin selection.

>>>>

The package also provides the a histogram function, which is a generalization
of \package{matplotlib}’s histogram function, to allow for more flexible
specification of histogram bins.  The function provides several methods of
automatically tuning the histogram bin size. It has a syntax identical to
\package{matplotlib}’s histogram function (with the exception of the bins
parameter), which allows specification of one of four different methods for
automatic bin selection.
